---
geometry: "left= 0.5 cm, right=0.5 cm, top=3.5 cm, bottom=2 cm"
output:
  pdf_document:
    fig_caption: FALSE
header-includes:
    \usepackage{wallpaper}
    \usepackage{color}
    \usepackage{multicol}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

\pagenumbering{gobble}

\CenterWallPaper{1}{images/Title.jpg}
\newpage\null\thispagestyle{empty}

\newpage
\ClearWallPaper

\CenterWallPaper{1}{images/Main_Page.jpg}
```{r,fig.align='center',results='asis'}
#Main Plot
Total_Nutrition <- c(".", ".")
Type <- c("Your Score", "Ideal Score")
Score <- c(subgroup$total_points, 50 - subgroup$total_points)
data <- data.frame(Total_Nutrition, Type, Score)
plot_title<-paste(subgroup$first_name,"'s", " Nutrition Report", sep="")
cat("\\vspace*{1 cm}")
ggplot(data, aes(x = Total_Nutrition, y = Score, fill = Type)) +
  geom_bar(stat = "identity") +
  ggtitle(plot_title) +
  xlab("Total Nutrition")+
  theme(plot.title = element_text(hjust = 0.5))

```

\vspace*{1 cm}

`r subgroup$first_name` has a total nutrition score of `r subgroup$total_points` out of 50 possible points. Read on to know what you are and aren't doing well and how you can get even better


\newpage
\CenterWallPaper{1}{images/Vegetables.jpg}
```{r, echo=FALSE, results='asis'}
#Vegetables
Vegetables <- c(".", ".")
Type <- c("You", "Ideal")
Score <- c(subgroup$vegetable_points, 5 - subgroup$vegetable_points)
data <- data.frame(Vegetables, Type, Score)
score_pc=subgroup$vegetable_points*20
```
 
\begin{multicols}{2}
 
```{r, fig.width=4, fig.height=3, fig.align='left', echo=FALSE, results='asis'}

ggplot(data, aes(x = Vegetables, y = Score, fill = Type)) +
  geom_bar(stat = "identity")+
  theme(
    plot.margin =  unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
    legend.margin=margin(l = 0,r = 0.1 ,b = 0.1, t=0.1, unit='cm'),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.title.y = 
    
    )
```

```{r, echo=FALSE, results='asis'}

if(score_pc==100){
  #Positive Result Recommendation  
  cat("Good Job. Keep up the good work and eat lots of veggies")
  
}else{
  #Negative Result Recommendation
  cat("1. Eat Veggies everyday")
  cat("\\newline ")
  cat("2. Make veggie chips in the microwave like pumpkin chips and spinach chips")
}
```

\end{multicols}

```{r, echo=FALSE, results='asis'}
if(score_pc==100){
  cat("\\vspace*{1.5cm}")
  cat("${}$\\hspace{14.15cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else if(score_pc<9){
  cat("\\vspace*{1.5 cm}")
  cat("${}$\\hspace{14.8cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else{
  cat("\\vspace*{1.2 cm}")
  cat("${}$\\hspace{14.5cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}

```

\newpage
\CenterWallPaper{1}{images/Fruits.jpg}
```{r, echo=FALSE, results='asis'}
#Fruit
Fruit <- c(".", ".")
Type <- c("You", "Ideal")
Score <- c(subgroup$fruit_points, 5 - subgroup$fruit_points)
data <- data.frame(Fruit, Type, Score)
score_pc=subgroup$fruit_points*20
```
 
\begin{multicols}{2}
 
```{r, fig.width=4, fig.height=3, fig.align='left', echo=FALSE, results='asis'}

ggplot(data, aes(x = Fruit, y = Score, fill = Type)) +
  geom_bar(stat = "identity")+
  theme(
    plot.margin =  unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
    legend.margin=margin(l = 0,r = 0.1 ,b = 0.1, t=0.1, unit='cm'),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.title.y = 
    
    )
```

```{r, echo=FALSE, results='asis'}

if(score_pc==100){
  #Positive Result Recommendation  
  cat("Good Job. Keep up the good work and eat lots of veggies")
  
}else{
  #Negative Result Recommendation
  cat("1. Eat Fruits everyday")
  cat("\\newline ")
  cat("2. Make Juice")
}
```

\end{multicols}

```{r, echo=FALSE, results='asis'}
if(score_pc==100){
  cat("\\vspace*{1.5cm}")
  cat("${}$\\hspace{14.15cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else if(score_pc<9){
  cat("\\vspace*{1.5 cm}")
  cat("${}$\\hspace{14.8cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else{
  cat("\\vspace*{1.2 cm}")
  cat("${}$\\hspace{14.5cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}

```

\newpage
\CenterWallPaper{1}{images/Exercise.jpg}
```{r, echo=FALSE, results='asis'}
#Exercise
Exercise <- c(".", ".")
Type <- c("You", "Ideal")
Score <- c(subgroup$exercise_points, 5 - subgroup$exercise_points)
data <- data.frame(Exercise, Type, Score)
score_pc=subgroup$exercise_points*20
```
 
\begin{multicols}{2}
 
```{r, fig.width=4, fig.height=3, fig.align='left', echo=FALSE, results='asis'}

ggplot(data, aes(x = Exercise, y = Score, fill = Type)) +
  geom_bar(stat = "identity")+
  theme(
    plot.margin =  unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
    legend.margin=margin(l = 0,r = 0.1 ,b = 0.1, t=0.1, unit='cm'),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.title.y = 
    
    )
```

```{r, echo=FALSE, results='asis'}

if(score_pc==100){
  #Positive Result Recommendation  
  cat("Good Job. Keep up the good work and eat lots of veggies")
  
}else{
  #Negative Result Recommendation
  cat("1. Eat Veggies everyday")
  cat("\\newline ")
  cat("2. Make veggie chips in the microwave like pumpkin chips and spinach chips")
}
```

\end{multicols}

```{r, echo=FALSE, results='asis'}
if(score_pc==100){
  cat("\\vspace*{1.5cm}")
  cat("${}$\\hspace{14.15cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else if(score_pc<9){
  cat("\\vspace*{1.5 cm}")
  cat("${}$\\hspace{14.8cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else{
  cat("\\vspace*{1.2 cm}")
  cat("${}$\\hspace{14.5cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}

```

\newpage
\CenterWallPaper{1}{images/Water.jpg}
```{r, echo=FALSE, results='asis'}
#Water
Water <- c(".", ".")
Type <- c("You", "Ideal")
Score <- c(subgroup$water_points, 5 - subgroup$water_points)
data <- data.frame(Water, Type, Score)
score_pc=subgroup$water_points*20
```
 
\begin{multicols}{2}
 
```{r, fig.width=4, fig.height=3, fig.align='left', echo=FALSE, results='asis'}

ggplot(data, aes(x = Water, y = Score, fill = Type)) +
  geom_bar(stat = "identity")+
  theme(
    plot.margin =  unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
    legend.margin=margin(l = 0,r = 0.1 ,b = 0.1, t=0.1, unit='cm'),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.title.y = 
    
    )
```

```{r, echo=FALSE, results='asis'}

if(score_pc==100){
  #Positive Result Recommendation  
  cat("Good Job. Keep up the good work and eat lots of veggies")
  
}else{
  #Negative Result Recommendation
  cat("1. Eat Veggies everyday")
  cat("\\newline ")
  cat("2. Make veggie chips in the microwave like pumpkin chips and spinach chips")
}
```

\end{multicols}

```{r, echo=FALSE, results='asis'}
if(score_pc==100){
  cat("\\vspace*{1.5cm}")
  cat("${}$\\hspace{14.15cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else if(score_pc<9){
  cat("\\vspace*{1.5 cm}")
  cat("${}$\\hspace{14.8cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else{
  cat("\\vspace*{1.2 cm}")
  cat("${}$\\hspace{14.5cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}

```

\newpage
\CenterWallPaper{1}{images/Dairy.jpg}
```{r, echo=FALSE, results='asis'}
#Dairy
Dairy <- c(".", ".")
Type <- c("You", "Ideal")
Score <- c(subgroup$dairy_points, 5 - subgroup$dairy_points)
data <- data.frame(Dairy, Type, Score)
score_pc=subgroup$dairy_points*20
```
 
\begin{multicols}{2}
 
```{r, fig.width=4, fig.height=3, fig.align='left', echo=FALSE, results='asis'}

ggplot(data, aes(x = Dairy, y = Score, fill = Type)) +
  geom_bar(stat = "identity")+
  theme(
    plot.margin =  unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
    legend.margin=margin(l = 0,r = 0.1 ,b = 0.1, t=0.1, unit='cm'),
    axis.ticks.x=element_blank(),
    axis.ticks.y=element_blank(),
    axis.title.y = 
    
    )
```

```{r, echo=FALSE, results='asis'}

if(score_pc==100){
  #Positive Result Recommendation  
  cat("Good Job. Keep up the good work and eat lots of veggies")
  
}else{
  #Negative Result Recommendation
  cat("1. Eat Veggies everyday")
  cat("\\newline ")
  cat("2. Make veggie chips in the microwave like pumpkin chips and spinach chips")
}
```

\end{multicols}

```{r, echo=FALSE, results='asis'}
if(score_pc==100){
  cat("\\vspace*{1.5cm}")
  cat("${}$\\hspace{14.15cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else if(score_pc<9){
  cat("\\vspace*{1.5 cm}")
  cat("${}$\\hspace{14.8cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}else{
  cat("\\vspace*{1.2 cm}")
  cat("${}$\\hspace{14.5cm} \\fontsize{40}{48}\\selectfont{\\textcolor{white}{",score_pc,"\\%","}","}","\\normalsize",sep="")  
}

```

\newpage
\CenterWallPaper{1}{images/Last_Page.jpg}
\newpage\null\thispagestyle{empty}